Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-05-26 paper.tex
abstract updated2

In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons. Many theoretical approaches have been applied to interpret the similarities. However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision. To further investigate these effects on the ridge effect, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at a center-of-mass energy $\sqrt{s} = 13$~TeV. A dedicated high-multiplicity trigger implemented in ALICE since 2016 is beneficial for the study because of increased statistics for high-multiplicity pp collisions.  The results are compared to previous measurements by other LHC experiments. In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
\end{titlepage}
\setcounter{page}{2}

>>>>

In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons. Many theoretical approaches have been applied to interpret the similarity. However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision. To further investigate these effects on the ridge effect, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.  The results are compared to previous measurements by other LHC experiments. In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
\end{titlepage}
\setcounter{page}{2}
